---
title: "hw5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
#Q1
income = c(102, 300, 102, 100, 205, 105, 71 , 92)
prob = c(0.125,0.125,0.125,0.125,0.125,0.125,0.125,0.125)
chisq.test(income, p = prob)
```
As the p-value is very small, the null hypothesis(all branches are operating the same) is rejected.
```{r a}
#Q2
mydata = data.frame(score = c(50, 50, 60, 70, 75, 80, 90, 85,55, 75, 80, 90, 105, 65),
                    treatment = factor(c(rep("Classical", 8), rep("Modern", 6))))
library(coin)
coin::oneway_test(score~treatment, data=mydata, distribution="exact")
```
As the p-value is 0.3, we can not reject null hypothesis(operation of both classical and Modern stores are the same)
```{r b}
#Q3
before = c(509, 517, 502, 629, 830, 911, 847, 803, 727, 853, 757, 730, 774, 718, 904)
after = c(517, 508, 523, 730, 821, 940, 818, 821, 842, 842, 709, 688, 787, 780, 901)
mydata = data.frame(score = c(before, after),
                    treatment = factor(c(rep("before", 15), rep("after", 15))))
wilcox.test(score~treatment, data = mydata)
```
As the p-value is 0.8, we can not reject null hypothesis(Advertisement has not increased the market sale of the branches)
```{r c}
#Q4
White = c(510, 720, 930, 754, 105)
Blue = c(925, 735, 753, 685)
Red = c(730, 745, 875, 610)
mydata = data.frame(score = c(White, Blue),
                    treatment = factor(c(rep("White", 5), rep("Blue", 4))))

wilcox.test(score~treatment, data = mydata)
```
Due to the large p value, we can not reject null hypothesis(two samples "White and Blue" come from the same population)
```{r d}
mydata = data.frame(score = c(White, Red),
                    treatment = factor(c(rep("White", 5), rep("Red", 4))))

wilcox.test(score~treatment, data = mydata)
```
Due to the large p value, we can not reject null hypothesis(two samples "White and Red" come from the same population)
```{r e}
mydata = data.frame(score = c(Blue, Red),
                    treatment = factor(c(rep("Blue", 4), rep("Red", 4))))

wilcox.test(score~treatment, data = mydata)
```
Due to the large p value, we can not reject null hypothesis(two samples "Blue and Red" come from the same population)

So finally we can not say that any special color has any meaningful difference in its sale.
```{r f}
#Q5
tv = read.csv("/Users/parnianshahkar/Desktop/tv.csv")
library(dplyr)
tv = data.matrix(tv)
friedman.test(tv)
```
Due to the large p value, we can not reject null hypothesis(advertisement does not effect on peoples satisfaction from a product)
```{r g}
#Q6
always = c(151, 802, 753)
sometimes = c(252, 603, 55)
never = c(603, 405, 408)
mat = matrix(c(always,sometimes, never), nrow = 3 )
chisq.test(mat)

```
Due to the small, we can reject null hypothesis(city size has no effect on usage of a product), so city has effect on usage of a product.
```{r h}
#Q7
cons = read.csv("/Users/parnianshahkar/Desktop/consumption.csv")
df = data.frame(score = c(cons[,1], cons[,2]),product =  c(rep("A", 100), rep("B", 100)))
wilcox.test(score~product, data = df)
```
Due to the small, we can reject null hypothesis, so there is a meaningful relationship between selling rate of these two products.
```{r j}
#Q8
Male = c(301, 353, 558)
Female = c(502, 155, 153)
mat = matrix(c(Male, Female), nrow = 2, byrow = TRUE)
print(chisq.test(mat))
```
Due to the small, we can reject null hypothesis,So Gender has a meaningful effect on the reason of buying stuff.



